Untitled

### 2024-11-13 code/manuscript_altanalysis.Rmd
Appendix Figures

  outlier.vals <- quantile(df.temptemp$Total, p = c(0.01, 0.99), na.rm = TRUE)
   event_study(data = df.temptemp %>% mutate(ifelse(Att == 2009, 0, Att)) %>% mutate(Total = ifelse(Total <= outlier.vals[1], outlier.vals[1], 
                            ifelse(Total >= outlier.vals[2], outlier.vals[2], Total))),
  yname = "Staff", idname = "ID", tname = "Year", gname = "Att", estimator = "all", xformla = ~Pct.NHA + Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.FarmWorker + Pct.Homeless + UrbanRuralFlag) %>%
  filter(abs(term) <= 7) %>%
  filter(estimator == "Gardner (2021)") %>%
  #filter(estimator == "Callaway and Sant'Anna (2020)") %>%
  ggplot(aes(x = term, y = estimate, color = estimator)) + geom_point(position = position_dodge(0.9), size = 3) + geom_errorbar(aes(ymin=estimate-1.96*std.error, ymax=estimate+1.96*std.error), width=.25, position = position_dodge(0.9), size = 0.8)  +
  #facet_wrap(~V1, scales = "free_y", ncol = 3) +
  theme_tufte_revised() + geom_vline(xintercept=-0.5, color="blue", linetype="dashed", alpha=.6)+ #theme(legend.position = "none", plot.title = element_text(size=18, face='bold')) +
  geom_hline(yintercept=0, color="black", linetype="dashed", alpha=.5) + ggtitle("Outcomes") + xlab("Year Relative to Competitive Shock") + ylab("Percentage Points")

>>>>

  outlier.vals <- quantile(df.temptemp$Altman, p = c(0.01, 0.99), na.rm = TRUE)
   event_study(data = df.temptemp %>% mutate(ifelse(Att == 2009, 0, Att)) %>% mutate(Altman = ifelse(Altman <= outlier.vals[1], outlier.vals[1], 
                            ifelse(Altman >= outlier.vals[2], outlier.vals[2], Altman))),
  yname = "Altman", idname = "ID", tname = "Year", gname = "Att", estimator = "all", xformla = ~Pct.NHA + Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.FarmWorker + Pct.Homeless + UrbanRuralFlag) %>%
  filter(abs(term) <= 7) %>%
  filter(estimator == "Gardner (2021)") %>%
  #filter(estimator != "Callaway and Sant'Anna (2020)") %>%
  ggplot(aes(x = term, y = estimate, color = estimator)) + geom_point(position = position_dodge(0.9), size = 3) + geom_errorbar(aes(ymin=estimate-1.96*std.error, ymax=estimate+1.96*std.error), width=.25, position = position_dodge(0.9), size = 0.8)  +
  #facet_wrap(~V1, scales = "free_y", ncol = 3) +
  theme_tufte_revised() + geom_vline(xintercept=-0.5, color="blue", linetype="dashed", alpha=.6)+ #theme(legend.position = "none", plot.title = element_text(size=18, face='bold')) +
  geom_hline(yintercept=0, color="black", linetype="dashed", alpha=.5) + ggtitle("Outcomes") + xlab("Year Relative to Competitive Shock") + ylab("Percentage Points")
